---
title: "Poverty and Priority Queueing"
author: "Marcos Gallo"
date: "2023/02/28"
format:
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
---

# Task Prioritization

```{r init, warning=FALSE, include=FALSE}

library(stringi)
library(stringr)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(latticeExtra)

```

## Priority Queuing

K: Explain with equations.

### Urgency and Importance

M: Explain (with equation for different weighting for warmth and competence)

#### Simulation

Simmer package:

```{r simmer-simulation}
#| fig-cap: Probability of Survival by Urgency Weight 

urgency_survival_grid <- read_csv("urgency-survival-grid.csv") %>%
  rename(time = mean_time) %>%
  filter(time < 25) # Anything greater is close to 0

levelplot(mean_survival ~ time * weight, urgency_survival_grid, 
          panel = panel.levelplot.points, cex = 0
    ) + 
    latticeExtra::layer_(panel.2dsmoother(..., n = 200))

```

```{r simmer-burstiness}
#| fig-cap: Burstiness by Urgency Weight 

urgency_burstiness_grid <- read_csv("urgency-burstiness-grid.csv") 

library(viridis)
ggplot(urgency_burstiness_grid,
       aes(x = M, y = B)) +
  geom_jitter(aes(color = weights),
              size = 1,
              alpha = 0.8) +
  labs(color = "Urgency Weight") +
  scale_color_viridis(option = "D") +
  geom_hline(yintercept = 0) +
  geom_hline(xintercept = 0)

```

## Relating to Poverty

K: role strain...

## Relating to Anxiety

M: proposal?

## Interactions

M: proposal?

# The Experiment

## Structure

K:

### Simulation

```{r dyn-pro-simulation-results}
#| fig-cap: Percentage of Urgent Choices

urgency_ratio_grid <- read_csv("urgency-ratio-grid.csv") 
urgency_ratio_grid <- urgency_ratio_grid %>%
  rename(gamma = `...1`) %>%
  pivot_longer(!gamma, names_to = "cost", values_to = "urgent") %>%
  mutate(cost = as.numeric(cost))

levelplot(urgent ~ cost * gamma, urgency_ratio_grid, 
          panel = panel.levelplot.points, cex = 0
    ) + 
    latticeExtra::layer_(panel.2dsmoother(..., n = 200))

```

## Data

```{r}

```

K:

### Demographics

K:

### Measures of Poverty

M: 2022 Report

#### Self-Reported Income

#### ZIP code Measures

#### Composite Measure (PCA)

### Behavioral Variables

#### Choice

K: "Difficult Choices"

#### Reaction Time

M:

### Accuracy

M: Report

K: explanation + histogram

## Results

### Trade-off Decisions

```{r trade-off-results}
#| label: trade-off-results
#| fig-cap: "Choice proportions by income and anxiety"
#| fig-subcap:
#|   - "Mturk, Income"
#|   - "Mturk, Anxiety"
#|   - "Prolific, Income"
#|   - "Prolific, Anxiety"
#| layout-ncol: 2
#| column: page-right



```

Accuracy in trade-off decisions as a function of income and anxiety

Multiple regression models to test the same hypotheses with different measures of income.

Percent of urgent choices (vs. important) as a function of income and anxiety.

### Reaction Time

### Accuracy

Distribution of accuracy

#### Accuracy, Anxiety, and Income

#### Note on Deterministic Choices

K: preliminary model. Continuous -\>

K

### Other Poverty Measures

# Recommendations

## Power Analysis

IRB

## Redesign

### Probabilistic Choice

IRB

### Flexible Queue Size

IRB

### Comprehensive Measures of Poverty

IRB

## Population

### Online Sample

Pros and cons.

### Homeless

M: Look Sera's studies

IRB: Justification

### Other Low SES Cohorts

M: Proposal

# Appendix {.unnumbered}

## Priority Queuing Simulation

## Dynamic Programming Simulation

## Bayesian Model for Cost Estimation

### Model

### Estimation

## Code

### Priority Queuing Simulation

```{r pri-q-simulation, eval=FALSE, include=TRUE}

library(simmer)
library(simmer.plot)
library(tidyverse)
library(latex2exp)
#library(dplyr)
#library(data.table)
set.seed(1234)

# Parameters
lambda <- 5
mu <- 5
t_simul <- 150 #Calibrated to optimize simulation time (prob_continue ≈ 0)
n_simul <- 2
scale = 100 # The scale on alpha to transfer runif(0,1) to something with more variance

weights <- seq(0, 1, by = 0.001)
arri <- list()
attr <- list()
total <- list()

# Simulations with simmer
for (w in 1:length(weights)) {
  env <- simmer("poverty")
  
  person <- trajectory("Poor's Trajectory") %>%
    set_attribute(keys = "urgency", function()
      runif(1, 0, 1)) %>%
    set_attribute(keys = "importance", function()
      runif(1, 0, 1)) %>%
    set_attribute(keys = "weight", weights[w]) %>%
    set_prioritization(function() {
      prio <-
        10000 * (
          get_attribute(env, "weight") * get_attribute(env, "urgency") +
            (1 - get_attribute(env, "weight")) * get_attribute(env, "importance")
        )
      c(prio, NA, NA)
    }) %>%
    # log_(function() {
    #   paste("Priority is: ", get_prioritization(env)[1])
    # }) %>%
    seize("person", amount = 1) %>%
    timeout(function()
      rexp(1, mu)) %>%
    release("person", amount = 1)
  
  env <-
    simmer() %>%
    add_resource("person", capacity = 1) %>%
    add_generator("Task", person, function()
      rexp(1, lambda), mon = 2)
  
  # env %>% run(until = t_simul)
  
  envs <- lapply(1:n_simul, function(i) {
    env %>%
      run(until = t_simul) %>%
      wrap()
  })
  
  ## Change Variables before
  arri[[w]] <- get_mon_arrivals(envs, ongoing = TRUE)
  attr[[w]] <- get_mon_attributes(envs)
  
  # Merge
  total[[w]] <-
    inner_join(arri[[w]], attr[[w]][attr[[w]]$key == "urgency", c(2, 4, 5)], by = c("name", "replication"))
  total[[w]] <-
    total[[w]] %>%
    rename(urgency = value)
  total[[w]] <-
    total[[w]][order(total[[w]]$replication, total[[w]]$start_time, decreasing = FALSE), ]
  row.names(total[[w]]) <- NULL
  total[[w]] <-
    inner_join(total[[w]], attr[[w]][attr[[w]]$key == "importance", c(2, 4, 5)], by = c("name", "replication"))
  total[[w]] <-
    total[[w]] %>%
    rename(importance = value)
  total[[w]] <-
    total[[w]][order(total[[w]]$replication, total[[w]]$start_time, decreasing = FALSE), ]
  row.names(total[[w]]) <- NULL
  total[[w]]$waiting_time <-
    total[[w]]$end_time - total[[w]]$start_time - total[[w]]$activity_time

    # Take care of precision problems yielding negative wait times.
  if (nrow(total[[w]][total[[w]]$waiting_time < 0 &
                      !is.na(total[[w]]$waiting_time), ]) > 0) {
    total[[w]][total[[w]]$waiting_time < 0 &
                 !is.na(total[[w]]$waiting_time), ]$waiting_time <- 0
  }

  #Weibull distribution with monomial function
  alpha = (scale - scale * as.numeric(total[[w]]$urgency)) #for now
  beta = 1
  total[[w]]$prob_fail <-
    1 - exp(-1 * (total[[w]]$waiting_time / alpha) ^ (beta))

  # Get probability of survival
  total[[w]] <- total[[w]] %>%
    mutate(prob_continue = (1 - prob_fail)) %>%
    group_by(replication) %>%
    mutate(prob_continue = lag(cumprod(prob_continue), k=1, default=1))

  cat('Simulation', w, 'of', length(weights), '\n')
}

sigma_list <- lapply(X = total, function(X)   sd(X[!is.na(X$waiting_time), ]$waiting_time))
mu_list    <- lapply(X = total, function(X) mean(X[!is.na(X$waiting_time), ]$waiting_time))
lag_time <- lapply(X = total, function(X) X %>%
                     filter(!is.na(waiting_time)) %>%
                     group_by(replication) %>%
                     mutate(waiting_time_lag = lag(waiting_time, default = 0)) %>%
                     dplyr::select(waiting_time, waiting_time_lag) %>%
                     cor())
memory   <- lapply(X = lag_time, function(X) X[2,3])


# Burstiness -------------------------------------------------------------
burstiness <- data.frame(weights) %>%
  mutate(sigma = unlist(sigma_list)) %>%
  mutate(mu = unlist(mu_list)) %>%
  mutate(B = (sigma - mu) / (sigma + mu)) %>%
  mutate(M = unlist(memory))

# Probability of Survival -------------------------------------------------
prob_survival <- lapply(X = total,
                        function(X) X %>%
                          group_by(name) %>%
                          summarise(mean_survival = mean(prob_continue),
                                    mean_time = mean(end_time)) %>%
                          rename(task = name) %>%
                          mutate(task = readr::parse_number(task))
                          )
names(prob_survival) <- weights
survival <- prob_survival %>%
  bind_rows(.id = "weight")

```

### Dynamic Programming Simulation

```{r dyn-pro-simulation, eval=FALSE, include=TRUE}

library(stringi)
library(stringr)

#Importance
imp <- c(1,2)
#Cost
cost1 = 0
cost2_grid <- seq(from = 0.1, to = 0.9, by = 0.05)
#Discounting
gamma_grid <- seq(from = 0.8, to = 1, by = 0.025)
#Choices
tasks <- c("HHU",
            "HH0",
            "HLU",
            "HL0",
            "LHU",
            "LH0",
            "LLU",
            "LL0")
tasks <- as.data.frame(tasks)
# Urgency Ratios
ratios <- c()

for (gamma in gamma_grid) {
  print(gamma)
  for (cost2 in cost2_grid) {
    # Add values
    tasks$value  <- c(imp[2]-cost2,
                      imp[2]-cost2,
                      imp[2]-cost1,
                      imp[2]-cost1,
                      imp[1]-cost2,
                      imp[1]-cost2,
                      imp[1]-cost1,
                      imp[1]-cost1)
    #Look up values
    r_choice <- tasks$value
    names(r_choice) <- tasks$tasks
    ## Use unname(r_choice["HH0"]) for example
    
    # States
    S <- as.data.frame(t(combn(tasks$tasks,2)))
    for (chr in tasks$tasks) {
      # Add states with two of the same task
      S <- rbind(S,c(chr,chr))
      # Add states with only one task transition to one task
      S <- rbind(S,c(chr,NA))
      # Add states with only one task transitioning to two tasks
      S <- rbind(S,c(chr,"TR"))
    }
    
    #Choice|States
    ## 1st column is choice.
    ## 1st+2nd columns are the state
    ch <- expand.grid(tasks$tasks,tasks$tasks)
    # Fix factor levels for next step
    levels(ch$Var2)
    levels(ch$Var2) = c("HHU", "HH0", "HLU", "HL0", "LHU", "LH0", "LLU", "LL0", "TR")
    for (chr in tasks$tasks) {
      ch <- rbind(ch,c(chr,NA))
      ch <- rbind(ch,c(chr,"TR"))
    }
    
    # Transition Probabilities
    choices <- paste(ch$Var1,ch$Var2,sep = "x")
    states <- paste(S$V1,S$V2,sep = "x")
    transitions <- expand.grid(choices,states)
    # Remaining task (last 3 characters) is in the next state, but no NA
    transitions$prob <- NA
    ## Non-urgent tasks:
    ## Note this is also transitioning to NA and TR states. Fix it in line 91 and __
    transitions[str_detect(str = str_sub(transitions$Var1,-3), pattern = "0"),]$prob <- 
      str_detect(str = transitions[str_detect(str = str_sub(transitions$Var1,-3), pattern = "0"),]$Var2,
                 pattern = str_sub(transitions[str_detect(str = str_sub(transitions$Var1,-3), pattern = "0"),]$Var1,-3))
    ## Urgent tasks: 
    ### If HXU -> LXU
    transitions[str_detect(str = str_sub(transitions$Var1,-1), pattern = "U") & 
                  str_detect(str = str_sub(transitions$Var1,start = -3, end = -3), pattern = "H"),]$prob <-
      str_detect(str = transitions[str_detect(str = str_sub(transitions$Var1,-1), pattern = "U") & 
                                     str_detect(str = str_sub(transitions$Var1,start = -3, end = -3), pattern = "H"),]$Var2,
                 pattern = paste("L",
                                 str_sub(transitions[str_detect(str = str_sub(transitions$Var1,-1), pattern = "U") & 
                                                       str_detect(str = str_sub(transitions$Var1,start = -3, end = -3), pattern = "H"),]$Var1,
                                         start = -2,
                                         end = -2),"U",sep = ""))
    ### If LXU -> NA
    ## first change all transitions to false
    transitions[str_detect(str = str_sub(transitions$Var2,-3), pattern = "NA"),]$prob <- FALSE
    # Now calculate other transitions
    transitions[str_detect(str = str_sub(transitions$Var1,-1), pattern = "U") & 
                  str_detect(str = str_sub(transitions$Var1,start = -3, end = -3), pattern = "L"),]$prob <-
      str_detect(str = transitions[str_detect(str = str_sub(transitions$Var1,-1), pattern = "U") & 
                                     str_detect(str = str_sub(transitions$Var1,start = -3, end = -3), pattern = "L"),]$Var2,
                 pattern = "NA")
    
    ## Single task with transition to single task:
    transitions[str_detect(str = transitions$Var1, pattern = "NA"),]$prob <-
      str_detect(str = transitions[str_detect(str = transitions$Var1, pattern = "NA"),]$Var2,
                 pattern = "TR")
    ## Single task with transition to single task:
    transitions[str_detect(str = transitions$Var1, pattern = "TR"),]$prob <- 0
    
    #Transforming them into probabilities by dividing by 8
    transitions$prob <- as.numeric(transitions$prob)
    transitions$prob <- transitions$prob / 8
    
    ## Single task with transition to single task:
    transitions[str_detect(str = transitions$Var1, pattern = "TR") &
                  str_length(transitions$Var2) == 7,]$prob <- 1/36
    
    ##################################################
    ################# Simulation
    ##################################################
    
    # Backwards induction
    ## Determine number of loops
    rounds = 20
    ## Create column with values of each choice for each round
    col_names <- paste("rd", c(1:rounds), sep = "")
    ch[col_names] <- NA
    ## Last round:
    ### fill in column in "ch" with the values
    for(choice in tasks$tasks) {
      ### first column is choice: find in tasks table the value of that choice
      ch[ch$Var1 == choice,rounds+2] <- tasks[tasks$tasks == choice,]$value
    }
    ### Multiply by discount factor^round
    ch[,rounds+2] <- ch[,rounds+2]*gamma^(rounds-1)
    
    
    ## Create state values for each round
    S[col_names] <- NA
    ### for each state in "S" choose the highest value in "ch" and create another column with the values
    best_option <- function(round, choice_matrix = ch, state_matrix = S, label_matrix = label){
      for(row in c(1:nrow(state_matrix))) {
        if (is.na(state_matrix[row,]$V2)) {
          state_matrix[row,round + 2] <- choice_matrix[choice_matrix$Var1 == state_matrix[row,]$V1 &
                                                         is.na(choice_matrix$Var2),round +2]
          label_matrix[row,round + 2] <- as.character(choice_matrix[choice_matrix$Var1 == state_matrix[row,]$V1 & 
                                                                      is.na(choice_matrix$Var2), 1])
        } else if (as.character(state_matrix[row,]$V2) == "TR") {
          state_matrix[row,round + 2] <- na.exclude(choice_matrix[choice_matrix$Var1 == state_matrix[row,]$V1 &
                                                                    choice_matrix$Var2 == state_matrix[row,]$V2,round + 2])
          label_matrix[row,round + 2] <- as.character(choice_matrix[choice_matrix$Var1 == state_matrix[row,]$V1 &
                                                                      is.na(choice_matrix$Var2), 1])
        } else {
          choice1 <- choice_matrix[choice_matrix$Var1 == state_matrix[row,]$V1 &
                                     choice_matrix$Var2 == state_matrix[row,]$V2 &
                                     !is.na(choice_matrix$Var2) &
                                     as.character(choice_matrix$Var2) != "TR",round +2]
          choice2 <- choice_matrix[choice_matrix$Var1 == state_matrix[row,]$V2 &
                                     choice_matrix$Var2 == state_matrix[row,]$V1 &
                                     !is.na(choice_matrix$Var2) &
                                     as.character(choice_matrix$Var2) != "TR",round +2]
          if (choice1 > choice2) {
            state_matrix[row,round + 2] <- choice1
            # ### save choices: change the suboptimal choices to NA
            # choice_matrix[choice_matrix$Var1 == state_matrix[row,]$V2 &
            #                 choice_matrix$Var2 == state_matrix[row,]$V1 &
            #                 !is.na(choice_matrix$Var2) &
            #                 as.character(choice_matrix$Var2) != "TR",round +2] <- NA
            label_matrix[row,round + 2] <- as.character(na.exclude(choice_matrix[choice_matrix$Var1 == state_matrix[row,]$V1 &
                                                                        choice_matrix$Var2 == state_matrix[row,]$V2, 1]))
          } else if (choice1 < choice2) {
            state_matrix[row,round + 2] <- choice2
            # ### save choices: change the suboptimal choices to NA
            # choice_matrix[choice_matrix$Var1 == state_matrix[row,]$V1 &
            #                 choice_matrix$Var2 == state_matrix[row,]$V2 &
            #                 !is.na(choice_matrix$Var2) &
            #                 as.character(choice_matrix$Var2) != "TR",round +2] <- NA
            label_matrix[row,round + 2] <- as.character(na.exclude(choice_matrix[choice_matrix$Var1 == state_matrix[row,]$V2 &
                                                                        choice_matrix$Var2 == state_matrix[row,]$V1, 1]))
          } else if (choice2 == choice1){
            state_matrix[row,round + 2] <- choice1
            label_matrix[row,round + 2] <- "either"
          }
        }
      }
      return(list(state_matrix,choice_matrix,label_matrix))
    }
    
    label <- S
    new_states_choices <- best_option(rounds)
    S <- new_states_choices[[1]]
    ch <- new_states_choices[[2]]
    label <- new_states_choices[[3]]
    ## second to last round to first round
    ### loop through the choices|states in "S"
    ### For each choice|state, calculate the the expected value
    
    # We need to change "transitions" for simplicity of search
    transitions$choice <- substr(transitions$Var1, 1, 3)
    transitions$non_choice <- substr(transitions$Var1, 5, 7)
    transitions[transitions$non_choice == "NA",]$non_choice <- NA
    transitions$state2_1 <- substr(transitions$Var2, 1, 3)
    transitions$state2_2 <- substr(transitions$Var2, 5, 7)
    transitions[transitions$state2_2 == "NA",]$state2_2 <- NA
    
    for(i in c(1:(rounds-1))){
      values <- S[,c(1,2,(rounds+3-i))]
      for(row in c(1:nrow(ch))){
        #### create probability vector P [44x1] from "transitions"
        if(!is.na(ch[row,2])) {
          prob_weight <- 
            transitions[ch[row,1] == transitions$choice &
                          ch[row,2] == transitions$non_choice &
                          !is.na(ch[row,2]) &
                          !is.na(transitions$non_choice),]
        } else if(is.na(ch[row,2])) {
          prob_weight <- 
            transitions[ch[row,1] == transitions$choice &
                          is.na(ch[row,2]) &
                          is.na(transitions$non_choice),]
        }
        
        #### Make sure "S" is in the same order [1x44]
        prob_weight <- merge(x = prob_weight,
                             y = values,
                             by.x = c("state2_1", "state2_2"),
                             by.y = c("V1", "V2"))
        prob_weight$weighted_value <- prob_weight$prob * values[,c(length(values))]
        ### Multiply by discount factor^round
        ch[row,rounds+2-i] <- gamma^(rounds-1-i)*tasks[tasks$tasks == ch[row,1],]$value + sum(prob_weight$weighted_value)
      }
      new_states_choices <- best_option(rounds-i)
      S <- new_states_choices[[1]]
      ch <- new_states_choices[[2]]
      label <- new_states_choices[[3]]
    }
    urgency <- apply(label[,-c(1:2)], 2, function(X) substr(X, nchar(X), nchar(X)))
    ratios <- append(ratios, table(urgency)["U"]/sum(table(urgency)))
  }
}

ratios_grid <- matrix(ratios,
                      nrow = length(gamma_grid),
                      ncol = length(cost2_grid),
                      dimnames = list(gamma_grid,
                                      cost2_grid))

### Export labels
write.csv(ratios_grid,"./urgency-ratio-grid.csv")

```

### Bayesian Model for Cost Estimation

#### Model

```{stan cost-model, eval=FALSE, include=TRUE, output.var="my_model"}
data {
  int<lower=1> N;
  int<lower=1> T;
  int<lower=2> nOpt;
  int<lower=1, upper=T> Tsubj[N];
  int<lower=0, upper=nOpt> choice[N, T]; //left or right?
  int<lower=0, upper=80> opt_st[N, T]; //option-state: an easy way to map the choices for choice prob calculation
  int value_lookup[80];
  int state_lookup[52, nOpt];
  matrix<lower=0, upper = 1>[80, 52] prob_weight;
  int<lower=0, upper=80> counterpart[80];
  // real outcome[N, T];  // no lower and upper bounds
}
transformed data {
  vector[nOpt] initV;  // initial values for EV
  initV = rep_vector(0.0, nOpt);
}
parameters {
// Declare all parameters as vectors for vectorizing
  // Hyper(group)-parameters
  vector[2] mu_pr;
  vector<lower=0>[2] sigma;

  // Subject-level parameters (for transformation from hyper to subj parameter)
  vector[N] costL;  // cost_low
  vector[N] costH;    // cost_high
}
model {
  // Hyperparameters
  mu_pr  ~ normal(0, 5); //weakly informative priors
  sigma ~ gamma(2,0.1); //weakly informative priors

  // individual parameters
  for (i in 1:N) {
    //tau[i]   = Phi_approx(mu_pr[1]  + sigma[1]  * tau_pr[i]); //approx Normal CDF + noise
    costL[i] ~ normal(mu_pr[1], sigma[1]);
    costH[i] ~ normal(mu_pr[2], sigma[2]);
  }

  // subject loop and trial loop
  for (i in 1:N) {
    vector[nOpt] ev; // expected value
    vector[4] value; // vector of value option, lookup table
    matrix[80, Tsubj[i]] ch; 
    matrix[52, Tsubj[i]] st;
    int round_back; // backwards counter for induction
    real weighted_value;
    
    ev = initV;

    // Declaring values for each option, lookup table (make it loop later)
    value[1] = 2 - costH[i];
    value[2] = 1 - costH[i];
    value[3] = 1 - costL[i];
    value[4] = 2 - costL[i];


    // Backwards induction
    //  fill in column in "ch" with the values
    for(option in 1:80) {
      // first column is choice: find in tasks table the value of that choice
      // lookup is a vector that tells you which cost correspondends to each choice
      ch[option, Tsubj[i]] = value[value_lookup[option]];
    }
    //    Create state values for each round
    // state_lookup tells you which choice|state maps onto which state
    // for each state in "S" choose the highest value in "ch" and create another column with the values
    for(state in 1:52) {
      if (ch[state_lookup[state,1], Tsubj[i]] >= ch[state_lookup[state,2], Tsubj[i]]) {
        st[state, Tsubj[i]] = ch[state_lookup[state,1], Tsubj[i]];
      } else if (ch[state_lookup[state,1], Tsubj[i]] < ch[state_lookup[state,2], Tsubj[i]]) {
        st[state, Tsubj[i]] = ch[state_lookup[state,2], Tsubj[i]];
      }
    }
        // compute action probabilities
        ev[1] = ch[opt_st[i, Tsubj[i]], Tsubj[i]];
        ev[2] = ch[counterpart[opt_st[i, Tsubj[i]]], Tsubj[i]];
        choice[i, Tsubj[i]] ~ categorical_logit(ev);
        
        for (t in 1:(Tsubj[i]-1)) {
          round_back = Tsubj[i] - t;
          for(option in 1:80) {
            // use action probabilities
            weighted_value = dot_product(prob_weight[option], col(st, (round_back + 1)) );
            ch[option, round_back] = value[value_lookup[option]] + weighted_value;
          }
          for(state in 1:52) {
            if (ch[state_lookup[state,1], round_back] >= ch[state_lookup[state,2], round_back]) {
              st[state, round_back] = ch[state_lookup[state,1], round_back];
            } else if (ch[state_lookup[state,1], round_back] < ch[state_lookup[state,2], round_back]) {
              st[state, round_back] = ch[state_lookup[state,2], round_back];
            }
          }
          // compute action probabilities
          ev[1] = ch[opt_st[i, round_back], round_back];
          ev[2] = ch[counterpart[opt_st[i, round_back]], round_back];
          choice[i, round_back] ~ categorical_logit(ev);
        }
  }
  
}
```

#### Model Data

```{r cost-model-data, eval=FALSE, include=TRUE}
# Data Wrangling ----------------------------------------------------------
load("Prolific-pilot1.Rdata")
data <- pilot1[!is.na(pilot1$participant),]
data <- data %>%
  group_by(participant) %>%
  mutate(COUNTER = row_number())
Tsubj <- data %>%
  group_by(participant) %>%
  summarize(n = n())

# Creating Choice set ----------------------------------------------------------
choices <- c("HHU", "HH0", "HLU", "HL0", "LHU", "LH0", "LLU", "LL0")
ch <- expand.grid(choices, choices)
# Fix factor levels for next step
levels(ch$Var2) = append(choices, "TR")
for (chr in choices) {
  ch <- rbind(ch,c(chr,NA))
  ch <- rbind(ch,c(chr,"TR"))
}

# Creating State set ----------------------------------------------------------
S <- as.data.frame(t(combn(choices,2)))
for (chr in choices) {
  # Add states with two of the same task
  S <- rbind(S,c(chr,chr))
  # Add states with only one task transition to one task
  S <- rbind(S,c(chr,NA))
  # Add states with only one task transitioning to two tasks
  S <- rbind(S,c(chr,"TR"))
}

# Create Transition Set ----------------------------------------------------------
# Transition Probabilities
choices <- paste(ch$Var1,ch$Var2,sep = "x")
states <- paste(S$V1,S$V2,sep = "x")
transitions <- expand.grid(choices,states)
# Remaining task (last 3 characters) is in the next state, but no NA
transitions$prob <- NA
## Non-urgent tasks:
## Note this is also transitioning to NA and TR states. Fix it in line 91 and __
transitions[str_detect(str = str_sub(transitions$Var1,-3), pattern = "0"),]$prob <- 
  str_detect(str = transitions[str_detect(str = str_sub(transitions$Var1,-3), pattern = "0"),]$Var2,
             pattern = str_sub(transitions[str_detect(str = str_sub(transitions$Var1,-3), pattern = "0"),]$Var1,-3))
## Urgent tasks: 
### If HXU -> LXU
transitions[str_detect(str = str_sub(transitions$Var1,-1), pattern = "U") & 
              str_detect(str = str_sub(transitions$Var1,start = -3, end = -3), pattern = "H"),]$prob <-
  str_detect(str = transitions[str_detect(str = str_sub(transitions$Var1,-1), pattern = "U") & 
                                 str_detect(str = str_sub(transitions$Var1,start = -3, end = -3), pattern = "H"),]$Var2,
             pattern = paste("L",
                             str_sub(transitions[str_detect(str = str_sub(transitions$Var1,-1), pattern = "U") & 
                                                   str_detect(str = str_sub(transitions$Var1,start = -3, end = -3), pattern = "H"),]$Var1,
                                     start = -2,
                                     end = -2),"U",sep = ""))
### If LXU -> NA
## first change all transitions to false
transitions[str_detect(str = str_sub(transitions$Var2,-3), pattern = "NA"),]$prob <- FALSE
# Now calculate other transitions
transitions[str_detect(str = str_sub(transitions$Var1,-1), pattern = "U") & 
              str_detect(str = str_sub(transitions$Var1,start = -3, end = -3), pattern = "L"),]$prob <-
  str_detect(str = transitions[str_detect(str = str_sub(transitions$Var1,-1), pattern = "U") & 
                                 str_detect(str = str_sub(transitions$Var1,start = -3, end = -3), pattern = "L"),]$Var2,
             pattern = "NA")

## Single task with transition to single task:
transitions[str_detect(str = transitions$Var1, pattern = "NA"),]$prob <-
  str_detect(str = transitions[str_detect(str = transitions$Var1, pattern = "NA"),]$Var2,
             pattern = "TR")
## Single task with transition to single task:
transitions[str_detect(str = transitions$Var1, pattern = "TR"),]$prob <- 0

#Transforming them into probabilities by dividing by 8
transitions$prob <- as.numeric(transitions$prob)
transitions$prob <- transitions$prob / 8

## Single task with transition to single task:
transitions[str_detect(str = transitions$Var1, pattern = "TR") &
              str_length(transitions$Var2) == 7,]$prob <- 1/36
# We need to change "transitions" for simplicity of search
transitions$choice <- substr(transitions$Var1, 1, 3)
transitions$non_choice <- substr(transitions$Var1, 5, 7)
transitions[transitions$non_choice == "NA",]$non_choice <- NA
transitions$state2_1 <- substr(transitions$Var2, 1, 3)
transitions$state2_2 <- substr(transitions$Var2, 5, 7)
transitions[transitions$state2_2 == "NA",]$state2_2 <- NA


# create choice[N,T] ----------------------------------------------------------
data$choice_bin <- 1
data[data$choice == "R",]$choice_bin <- 2
choice <- data %>%
  select(participant, COUNTER, choice_bin) %>%
  group_by(COUNTER) %>%
  spread(COUNTER, choice_bin)
# Take NAs out
choice[is.na(choice)] <- 0


# Option-State ------------------------------------------------------------
## an easy way to map the choices for choice prob calculation
ch_opt_translation <- ch[,c(1:2)]
ch_opt_translation$index <- c(1:length(ch_opt_translation$Var1))
ch_opt_translation$i1 <- NA
ch_opt_translation$e1 <- NA
ch_opt_translation$i2 <- NA
ch_opt_translation$e2 <- NA

ch_opt_translation$u1 <- grepl("U", ch_opt_translation$Var1)
ch_opt_translation$u2 <- grepl("U", ch_opt_translation$Var2)
ch_opt_translation[is.na(ch_opt_translation$Var2), ]$u2 <- NA
ch_opt_translation$u1 <- as.numeric(ch_opt_translation$u1) + 1
ch_opt_translation$u2 <- as.numeric(ch_opt_translation$u2) + 1

ch_opt_translation$i1 <- ifelse(substring(ch_opt_translation$Var1, 1, 1) == "H", 2, 1)
ch_opt_translation$i2 <- ifelse(substring(ch_opt_translation$Var2, 1, 1) == "H", 2, 1)
ch_opt_translation[is.na(ch_opt_translation$Var2), ]$i2 <- NA

ch_opt_translation$e1 <- ifelse(substring(ch_opt_translation$Var1, 2, 2) == "H", 2, 1)
ch_opt_translation$e2 <- ifelse(substring(ch_opt_translation$Var2, 2, 2) == "H", 2, 1)
ch_opt_translation[is.na(ch_opt_translation$Var2), ]$e2 <- NA

ch_opt_translation[grepl("TR", ch_opt_translation$Var2), ]$i2 <- 
  ch_opt_translation[grepl("TR", ch_opt_translation$Var2), ]$i1
ch_opt_translation[grepl("TR", ch_opt_translation$Var2), ]$e2 <- 
  ch_opt_translation[grepl("TR", ch_opt_translation$Var2), ]$e1
ch_opt_translation[grepl("TR", ch_opt_translation$Var2), ]$u2 <- 
  ch_opt_translation[grepl("TR", ch_opt_translation$Var2), ]$u1

ch_opt_translation[grepl("TR", ch_opt_translation$Var2), ]$i1 <- NA
ch_opt_translation[grepl("TR", ch_opt_translation$Var2), ]$e1 <- NA
ch_opt_translation[grepl("TR", ch_opt_translation$Var2), ]$u1 <- NA

data <- merge(x = data,
              y = ch_opt_translation[,-c(1:2)],
              by = c("u1", "u2", "e1", "e2", "i1", "i2"))

opt_st <- data %>%
  select(participant, COUNTER, index) %>%
  group_by(COUNTER) %>%
  spread(COUNTER, index)
# Take NAs out
opt_st[is.na(opt_st)] <- 0

ch_opt_translation$value <- 0
ch_opt_translation[grepl("HH", ch_opt_translation$Var1),]$value = 1
ch_opt_translation[grepl("LH", ch_opt_translation$Var1),]$value = 2
ch_opt_translation[grepl("LL", ch_opt_translation$Var1),]$value = 3
ch_opt_translation[grepl("HL", ch_opt_translation$Var1),]$value = 4


S$st_index <- c(1:nrow(S))
S <- merge(x = S,
           y = ch_opt_translation[,c(1:3)],
           by.x = c("V1", "V2"),
           by.y = c("Var1", "Var2"))
ch_opt_translation$index2 <- ch_opt_translation$index
S <- merge(x = S, 
           y = ch_opt_translation[,c(1:2,11)],
           by.x = c("V2", "V1"),
           by.y = c("Var1", "Var2"),
           all.x = TRUE)
state_lookup <- S %>%
  select(st_index, index, index2)
# Take NAs out
state_lookup[is.na(state_lookup$index2),]$index2 <- state_lookup[is.na(state_lookup$index2),]$index
# Order state_lookup
state_lookup <- state_lookup %>%
  arrange(order_by = st_index)

prob_weight <- merge(x = transitions,
                      y = ch_opt_translation[,c(1:3)],
                      by.x = c("choice", "non_choice"),
                      by.y = c("Var1", "Var2"))
prob_weight <- merge(x = prob_weight,
                     y = ch_opt_translation[,c(1:2,11)],
                     by.x = c("state2_1", "state2_2"),
                     by.y = c("Var1", "Var2"))


# Map Choices to States ---------------------------------------------------
choice_state <- as.data.frame(c(1:80))
choice_state <- merge(x = choice_state,
                      y = state_lookup[,-c(3)],
                      by.x = c("c(1:80)"),
                      by.y = c("index"),
                      all.x = TRUE)
choice_state <- merge(x = choice_state,
                      y = state_lookup[,-c(2)],
                      by.x = c("c(1:80)"),
                      by.y = c("index2"),
                      all.x = TRUE)
choice_state$st_index <- choice_state$st_index.x
choice_state[is.na(choice_state$st_index.x),]$st_index <- choice_state[is.na(choice_state$st_index.x),]$st_index.y
choice_state <- choice_state %>%
  select(`c(1:80)`, st_index)
prob_weight <- merge(x=prob_weight,
                     y=choice_state,
                     by.x = "index2",
                     by.y= "c(1:80)")
prob_weight <- prob_weight %>%
  select(index, st_index, prob)

prob_weight <- prob_weight %>%
  group_by(index) %>%
  spread(st_index, prob)


# Counterpart choice|states -----------------------------------------------
counterpart <- merge(x = choice_state, y = state_lookup[,-c(1)], by.x = "c(1:80)", by.y = "index", all.x = TRUE)
counterpart <- merge(x = counterpart, y = state_lookup[,-c(1)], by.x = "c(1:80)", by.y = "index2", all.x = TRUE)
counterpart$index_ALL <- counterpart$index
counterpart[is.na(counterpart$index),]$index_ALL <- counterpart[is.na(counterpart$index),]$index2
counterpart <- counterpart %>%
  select(index_ALL)

model_data <- list( N = length(unique(data$participant)), #number of part
                    T = max(data$COUNTER), # number of max rounds
                    nOpt = 2,
                    Tsubj = Tsubj$n, # number of round
                    choice = choice[,c(-1)],
                    opt_st = opt_st[,c(-1)],
                    value_lookup = ch_opt_translation$value,
                    state_lookup = state_lookup[,c(-1)],
                    prob_weight = prob_weight[,c(-1)],
                    counterpart = counterpart$index_ALL) # transition probabilities

```

#### Estimation

```{r cost-model-estimation, eval=FALSE, include=TRUE}

load("prolific1StanData.Rdata")
# my_model <- stan_model(file = "recipes/hier-bayes-simple.stan", verbose = TRUE)
Prolific1_Stan_results <- sampling(object = my_model, data = model_data,
                                   iter = 1000,
                                   chains = 1,
                                   cores = 3)

```
